---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# DMSS

<!-- badges: start -->
<!-- badges: end -->

Differential Misclassification considering Specificity and Sensitivity (**DMSS**) model uses binary regression models to fit the covariate-related sensitivity and specificity simultaneously for the observed response.

## Installation

You can install the development version of DMSS from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("AnqiWang2021/DMSS")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(DMSS)
library(rje)
# Generate the predictor variable and covariates
 X = rnorm(10000)
 L = rnorm(10000)
 V = rnorm(10000)
# Generate the covariate-related sensitivity and specificity
 theta = c(-2,3)
 p_Dtrue = expit(cbind(1,X)%*% theta)
 beta = c(0.45,0.5)
 sensitivity = expit(cbind(1,V)%*% beta)
 gamma = c(4.5,1)
 specificity = expit(cbind(1,L)%*% gamma)

# Generate the observed outcome variable
 p_Dstar = (1-specificity)+(specificity+sensitivity -1)*p_Dtrue
 Dstar = rbinom(10000,1,p_Dstar)
 
# initial value
 start = c(-1,1,0,0,3,0)
 result = loglik_EM (Dstar,X,V,L,start,tol = 1e-8, maxit = 1000)


```

